---
title: "Lab 04 - Visualizing Spatial Data"
author: "Anahatt Virk"
date: "06/26/25"
output: github_document
---

### Load packages and data
```{r dsbox}
install.packages("devtools", repos = "https://cloud.r-project.org")
devtools::install_github("tidyverse/dsbox")
```

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

The Denny's dataset has `r nrow(dennys)` rows and `r ncol(dennys)` columns. Each row represents one Denny's location and the variables are address, city, state, zipcode, longitude, and latitude. 

### Exercise 2

The La Quinta dataset has `r nrow(laquinta)` rows and `r ncol(laquinta)` columns. Each row represents one La Quinta location and the variables are address, city, state, zipcode, longitude, and latitude. 

### Exercise 3

From looking at the websites, it seems that there are La Quinta hotels outside of the U.S. These countries include Canada, Mexico, China, New Zealand, Georgia, Turkey, UAE, Chile, Colombia, and Ecuador. On the other hand, Denny's does Denny’s has locations in countries such as `r paste(unique(dennys$state[!dennys$state %in% state.abb]), collapse = ", ")` (if any).

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

