---
title: "Lab 04 - Visualizing Spatial Data"
author: "Anahatt Virk"
date: "06/26/25"
output: github_document
---

### Load packages and data
```{r dsbox}
install.packages("devtools", repos = "https://cloud.r-project.org")
devtools::install_github("tidyverse/dsbox")
```

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

The Denny's dataset has `r nrow(dennys)` rows and `r ncol(dennys)` columns. Each row represents one Denny's location and the variables are address, city, state, zipcode, longitude, and latitude. 

### Exercise 2

The La Quinta dataset has `r nrow(laquinta)` rows and `r ncol(laquinta)` columns. Each row represents one La Quinta location and the variables are address, city, state, zipcode, longitude, and latitude. 

### Exercise 3

From looking at the La Quinta website, there are La Quinta hotels outside of the U.S. These countries include Canada, Mexico, China, New Zealand, Georgia, Turkey, UAE, Chile, Colombia, and Ecuador. On the other hand, from looking at the Denny's website it seems that they only have locations in the U.S. 

### Exercise 4

One way to determine whether either establishment has locations outside of the U.S. by looking at the data is to filter by country by using code. This way, you are able to pull out all locations that are not in the United States. 

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

